### 2019-08-28 README.Rmd
added Travis badge
Added gene numbers to plot legend and removed devel from travis yaml

[![Travis build status](https://travis-ci.com/SabaLab/diffEnrich.svg?branch=master)](https://travis-ci.com/SabaLab/diffEnrich)

@@

*plotFoldEnrichment* generates a grouped bar plot using ggplot2 and the
*ggnewscale* package. KEGG pathways are plotted on the y-axis and fold
enrichment is plotted on the x-axis. each KEGG pathway has a bar plotting
its fold enrichment in list 1 (red) and its fold enrichment in list 2 (blue).
The transparency of the bars correspond to the adjusted p-value (FDR) for the
pathway's enrichment in the given list. The p-value presented as text to the
right of each pair of bars is the adjusted p-value (user defined: default is FDR) associated with the
differential enrichment of the pathway between the two lists, and the pathways
are ordered from top to bottom by this p-value (i.e. smallest p-value on top
of plot, and largest p-value on bottom of plot).

>>>>

[![Build Status](https://travis-ci.com/SabaLab/diffEnrich.svg?token=M2jELEzTYYqmxZMY6hpb&branch=master)](https://travis-ci.com/SabaLab/diffEnrich)

@@

*plotFoldEnrichment* generates a grouped bar plot using ggplot2 and the
*ggnewscale* package. KEGG pathways are plotted on the y-axis and fold
enrichment is plotted on the x-axis. each KEGG pathway has a bar plotting
its fold enrichment in list 1 (red) and its fold enrichment in list 2 (blue).
The transparency of the bars correspond to the adjusted p-value (FDR) for the
pathway's enrichment in the given list. The p-value presented as text to the
right of each pair of bars is the adjusted p-value (user defined: default is FDR) associated with the
differential enrichment of the pathway between the two lists, and the pathways
are ordered from top to bottom by this p-value (i.e. smallest p-value on top
of plot, and largest p-value on bottom of plot). Finally, the number of genes used
for analysis from each gene list (recall that this number may not be the same as the number of
genes in the user's original list) are reported below their repsective p-values
in the legend.
